
1. the top three factors that contribute to turnover
```{r}
library(dplyr)
df_hr=read.csv("CaseStudy2_data.csv")
dim(df_hr)
head(df_hr)
```
I guess top 3 is JobRole, MonthlyIncome, OverTime. Let's check it.

check the plausible factors related to attrition ; monthly income, job role, overtime, travel
```{r}
ggplot(df_hr, aes(x=JobRole, fill=Attrition)) + geom_bar(position = "fill")
ggplot(df_hr, aes(x=OverTime, fill=Attrition)) + geom_bar(position = "fill")
ggplot(df_hr, aes(x=BusinessTravel, fill=Attrition)) + geom_bar(position = "fill")


ggplot(df_hr, aes(x=MonthlyIncome, fill=Attrition)) + geom_bar(position = "fill")

```
Jobrole, overtime and business travel gives good idea but monthly income doesn't cause too many categories. I want to check one thing before re-define income level.
BTW, These factors are also related to the Attrition. interesting.
(MaritalStatus, JobSatisfaction, JobInvolvement, JobLevel,EnvironmentSatisfaction,Education,Age)

median income per jobrole
```{r}
hello1 <- df_hr %>% group_by(JobRole) %>% summarize(meanIncome = mean(MonthlyIncome), count = n()) %>% arrange(meanIncome)
print(hello1)
barplot(hello1$meanIncome, names.arg = hello1$JobRole)
```
this gives good idea that the income is highly related with job role. And there are three levels of income here. under 50k, 50k~100k, over 100k.I will recast montlhyincome for only attrition prediction not salary prediction.


re-define categorical variables like BusinessTravel,Department, EducationField, Gender,JobRole,MaritalStatus,OverTime, etc
Gender first! cause only two types for now.

Male is 1 
```{r}
library("stringr")
df_Gender <- 1*str_detect(df_hr$Gender, "Male")
df_cv=df_hr
df_cv$Gender<-df_Gender
head(df_cv)
```
BusinessTravel
Travel_rarely:0
Travel_Frequently:1
Non-Travel:2
```{r}
df_BusinessTravel = ifelse(str_detect(df_hr$BusinessTravel,"Travel_Rarely")==TRUE,"0",ifelse(str_detect(df_hr$BusinessTravel,"Travel_Frequently")==TRUE,"1","2"))
df_cv$BusinessTravel<-df_BusinessTravel
head(df_cv)
```
attrition
No is 1
```{r}
df_Attrition <- 1*str_detect(df_hr$Attrition, "No")
df_cv$Attrition<-df_Attrition
head(df_cv)
```


Sales 0
Research & Development	1
Human Resources 2
```{r}

df_Department = ifelse(str_detect(df_hr$Department,"Sales")==TRUE,"0",ifelse(str_detect(df_hr$Department,"Research & Development")==TRUE,"1","2"))
df_cv$Department<-df_Department

head(df_cv)
```

Healthcare Representative 1
Human Resources 2
Laboratory Technician 3
Manager 4
Manufacturing Director 5
Research Director 6
Research Scientist 7
Sales Executive 8
Sales Representative 9
```{r}
df_cv$JobRole<-as.integer(factor(df_hr$JobRole, levels = c("Healthcare Representative", "Human Resources","Laboratory Technician","Manager","Manufacturing Director","Research Director","Research Scientist","Sales Executive","Sales Representative")))
head(df_cv)
```

```{r}
df_cv$MaritalStatus<-as.integer(factor(df_hr$MaritalStatus, levels = c("Divorced", "Married","Single")))
head(df_cv)
```
Over18
Yes 1
No 2
```{r}
df_cv$Over18<-as.integer(factor(df_hr$Over18, levels = c("Y", "N")))
head(df_cv)
```
OverTime
Yes 1
No 2
```{r}
df_cv$OverTime<-as.integer(factor(df_hr$OverTime, levels = c("Yes", "No")))
head(df_cv)
```

EducationField
```{r}
ggplot(df_hr, aes(x=EducationField, fill=Attrition)) + geom_bar(position = "fill")
```
Life Sciences 1
Medical 2
Marketing 3
Technical Degree 4
Human Resources 5
Other 6
```{r}
df_cv$EducationField<-as.integer(factor(df_hr$EducationField, levels = c("Life Sciences", "Medical","Marketing","Technical Degree","Human Resources","Other")))
head(df_cv)
```

correlation map for attrition
```{r}
library(GGally)
# Convert data to numeric
corr <- data.frame(lapply(df_cv, as.integer))
corr$new <- corr$Attrition
# Plot the graph
plot_attrition=ggcorr(corr,
    method = c("pairwise", "spearman"),
    nbreaks = 6,
    hjust = 0.8,
    label = TRUE,
    label_size = 2,
    label_round = 4,
    color = "grey50")
plot_attrition
```
overtime 0.27, #1

monthly income, .1995

it will be better to re-scale the monthly income and check.
```{r}
for (x in 1:nrow(df_hr)) {
  if(df_hr$MonthlyIncome[x]<1000){df_MonthlyIncome[x] = 1}
  else if(df_hr$MonthlyIncome[x]>=1000 & df_hr$MonthlyIncome[x]<2000){df_MonthlyIncome[x] = 2}
  else if(df_hr$MonthlyIncome[x]>=2000 & df_hr$MonthlyIncome[x]<3000){df_MonthlyIncome[x] = 3}
  else if(df_hr$MonthlyIncome[x]>=3000 & df_hr$MonthlyIncome[x]<4000){df_MonthlyIncome[x] = 4}
  else if(df_hr$MonthlyIncome[x]>=4000 & df_hr$MonthlyIncome[x]<5000){df_MonthlyIncome[x] = 5}
  else if(df_hr$MonthlyIncome[x]>=5000 & df_hr$MonthlyIncome[x]<6000){df_MonthlyIncome[x] = 6}
  else if(df_hr$MonthlyIncome[x]>=6000 & df_hr$MonthlyIncome[x]<7000){df_MonthlyIncome[x] = 7}
  else if(df_hr$MonthlyIncome[x]>=7000 & df_hr$MonthlyIncome[x]<8000){df_MonthlyIncome[x] = 8}
  else if(df_hr$MonthlyIncome[x]>=8000 & df_hr$MonthlyIncome[x]<9000){df_MonthlyIncome[x] = 9}
  else if(df_hr$MonthlyIncome[x]>=9000 & df_hr$MonthlyIncome[x]<10000){df_MonthlyIncome[x] = 10}
  else if(df_hr$MonthlyIncome[x]>=10000 & df_hr$MonthlyIncome[x]<11000){df_MonthlyIncome[x] = 11}
  else if(df_hr$MonthlyIncome[x]>=11000 & df_hr$MonthlyIncome[x]<12000){df_MonthlyIncome[x] = 12}
  else if(df_hr$MonthlyIncome[x]>=12000 & df_hr$MonthlyIncome[x]<13000){df_MonthlyIncome[x] = 13}
  else if(df_hr$MonthlyIncome[x]>=13000 & df_hr$MonthlyIncome[x]<14000){df_MonthlyIncome[x] = 14}
  else if(df_hr$MonthlyIncome[x]>=14000 & df_hr$MonthlyIncome[x]<15000){df_MonthlyIncome[x] = 15}
  else if(df_hr$MonthlyIncome[x]>=15000 & df_hr$MonthlyIncome[x]<16000){df_MonthlyIncome[x] = 16}
  else if(df_hr$MonthlyIncome[x]>=16000 & df_hr$MonthlyIncome[x]<17000){df_MonthlyIncome[x] = 17}
  else if(df_hr$MonthlyIncome[x]>=17000 & df_hr$MonthlyIncome[x]<18000){df_MonthlyIncome[x] = 18}
  else if(df_hr$MonthlyIncome[x]>=18000 & df_hr$MonthlyIncome[x]<19000){df_MonthlyIncome[x] = 19}
  else if(df_hr$MonthlyIncome[x]>=19000 & df_hr$MonthlyIncome[x]<20000){df_MonthlyIncome[x] = 20}
else {df_MonthlyIncome[x] = 8}

}
df_re=df_hr
df_re$MonthlyIncomeLevel <- df_MonthlyIncome
ggplot(df_re, aes(x=MonthlyIncomeLevel, fill=Attrition)) + geom_bar(position = "fill")
```
let's check correlation again
```{r}
# Convert data to numeric
df_re=df_cv
df_re$MonthlyIncomeLevel <- df_MonthlyIncome
corr <- data.frame(lapply(df_re, as.integer))
corr$new <- corr$Attrition
# Plot the graph
plot_attrition=ggcorr(corr,
    method = c("pairwise", "spearman"),
    nbreaks = 6,
    hjust = 0.8,
    label = TRUE,
    label_size = 2,
    label_round = 4,
    color = "grey50")
plot_attrition
```
ohh .1992. interesting. #4
marrital status, .198 #5
total working year, .1996 #3
stock option level, .201 #2
overtime .27



2. interesting trends and observations from your analysis



there will be intended highly turnover rate position.

salary always number 1 factor of retrition so it will be the last choice to reduce retrition. 
hire more people or promotion and productivity increasing are good way to go

overtime 0.27, #1
marrital status, .198 #5
total working year, .1996 #3
stock option level, .201 #2
monthly income .1992. interesting. #4
will be good


correlation map for monthly income
```{r setup, include=FALSE}
library(GGally)
# Convert data to numeric
corr <- data.frame(lapply(df_cv, as.integer))
#make easier to see
corr$new <- corr$MonthlyIncome
# Plot the graph
income=ggcorr(corr,
    method = c("pairwise", "spearman"),
    nbreaks = 6,
    hjust = 0.8,
    label = TRUE,
    label_size = 3,
    color = "grey50")
income
```
joblevel .9
total working year .7
years at company .5

correlation network
```{r}
library(qgraph)
#use cor function to create a correlation matrix with milan.mort dataset
#and put into cormat variable
###################################################
corr1 <- data.frame(lapply(df_cv, as.integer))
cormat=cor(corr1)  #correlation matrix generated
###################################################
###################################################
#now plot a graph of the correlation matrix
###################################################
#qgraph(cormat, shape="circle", posCol="darkgreen", negCol="darkred", layout="groups", vsize=10)
qgraph(cormat, shape="circle", posCol="darkgreen", negCol="darkred", layout="spring", vsize=5)
head(df_cv)
```
lets make rshiny with this


3. predict attrition
GLM

rescale
```{r}
df_res <- df_cv %>%
	mutate_if(is.numeric, list(~as.numeric(scale(.))))
head(df_res)
dim(df_res)
```
exclude ID,EmployeeNumber will be bettter. not needed.

70/30
```{r}
#70/30 training/
# Loop for many k and the average of many training / test partition
hello_scale=df_cv

set.seed(300)
iterations = 1
numks = 1
splitPerc = .70

masterAcc = matrix(nrow = iterations, ncol = numks)


for(j in 1:iterations)
{
  trainIndices = sample(1:dim(hello_scale)[1],round(splitPerc * dim(hello_scale)[1]))
  train = hello_scale[trainIndices,]
  test = hello_scale[-trainIndices,]
  for(i in 1:numks)
  {formula = Attrition ~ Age + BusinessTravel + Department + Education + JobLevel + JobRole + MonthlyIncome + NumCompaniesWorked  + OverTime  + StockOptionLevel + TotalWorkingYears + YearsAtCompany + StockOptionLevel + YearsWithCurrManager + YearsInCurrentRole
classifications =  glm(formula, data = train, family = binomial())
  }
  
}
summary(classifications)
predicted <- predict(classifications, test, type = 'response')
```


accuracy
```{r}

# confusion matrix
table_mat <- table(test$Attrition, predicted>0.5)
table_mat
TP = table_mat[1,1]
FP = table_mat[1,2]
FN = table_mat[2,1]
TN = table_mat[2,2]
accuracy = (TN+TP)/(TN+TP+FP+TP)
accuracy
sensitivity = TP/(TP+FN)
sensitivity
specificity = TN/(TN+FP)
specificity
```
confusion matrix in caret threshold default is .5
https://www.rdocumentation.org/packages/InformationValue/versions/1.2.3/topics/confusionMatrix
rank-deficient fit. job level and monthly income has .9 correlation and I guess this make trouble. change formula
p-value



4. predict salary
let's change model to linear mod
```{r}
library("caret")
linearMod <- lm(train$MonthlyIncome ~ JobLevel + TotalWorkingYears + YearsAtCompany, data=train)
# 
summary(linearMod)
# now use it to predict the salary


predict = predict(linearMod, test, inverval="predict")


RMSE(test$MonthlyIncome,predict)
```