#Live Session 4 For Live Session Web Scraping Code
```{r}
library(XML) #xml_Parse
library(dplyr)
library(tidyr)
library(stringi)
library(rvest) #html_table, html_node
library(ggplot2)
library(RCurl) #getURL

#Basics of Scraping XML

# Method 1: XML

data <-getURL("https://www.w3schools.com/xml/simple.xml")
doc <- xmlParse(data)
names <- xpathSApply(doc,"//name",xmlValue)
price <- xpathSApply(doc,"//price",xmlValue)
description <- xpathSApply(doc,"//description",xmlValue)
bfasts = data.frame(names,price,description)
bfasts
bfasts$description
length(grep("covered",bfasts$description))
grepl("covered",bfasts$description)
sum(grepl("covered",bfasts$description))
which(grepl("covered",bfasts$description))
```

```{r}
# Method 2: rvest

hp<-read_html("https://www.w3schools.com/xml/simple.xml")
hp_nameR <- html_nodes(hp,"name")
hp_priceR <- html_nodes(hp,"price")
hp_descR <- html_nodes(hp,"description")
hp_nameR
hp_name = stri_sub(hp_nameR,7,-8)
hp_name
hp_price = stri_sub(hp_priceR,8,-9)
hp_price
hp_desc = stri_sub(hp_descR,14,-15)
hp_desc
bfast = data.frame(hp_name,hp_price,hp_desc)
grep("toast", bfast$hp_desc)
grepl("toast",bfast$hp_desc)

sum(grepl("toast",bfast$hp_desc))
```

```{r}
#Part 1: Restaurant Data from Baltimore!

# 1-1. Scrape the XML page for name, zipcode and city council district.  (Use either the XML or rvest package.)
library(XML) #xml_Parse
library(dplyr)
library(tidyr)
library(stringi)
library(rvest) #html_table, html_node
library(ggplot2)
library(RCurl) #getURL
fileURL<-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"

fileURL2 <- sub('https', 'http', fileURL)
doc <- xmlTreeParse(fileURL2, useInternal = TRUE)
```

```{r}
#1-2. Make a dataframe with just those columns.
names <- xpathSApply(doc,"//name",xmlValue)
zipcode <- xpathSApply(doc,"//zipcode",xmlValue)
councildistrict <- xpathSApply(doc,"//councildistrict",xmlValue)
bfasts = data.frame(names,zipcode,councildistrict)
bfasts
```

```{r}
#1-3. Are there any Sushi restaurants in Baltimore? (Where the dataset is from.)
length(grep("SUSHI",bfasts$names))
length(grep("JAPANESE",bfasts$names))
```

```{r}
#1-4. If so, can you estimate how many?
print('9~10')
```
```{r}
##1-5. Filter the dataframe for just downtown restaurants (Council District 11). 
df <- filter(bfasts,councildistrict == "11")
df
```

```{r}
##1-6. Are there any Sushi restaurants downtown?  # research the “grep” function
length(grep("SUSHI",df$names))
length(grep("JAPANESE",df$names))

```
```{r}
##1-7. If so, estimate how many “Sushi” restaurants are in Downtown
print('1')
```

```{r}
##1.8.Make a barplot of the estimated number of restaurants (Sushi or otherwise) in each council.
hello1 <- bfasts %>% group_by(councildistrict) %>% summarize(, count = n())
hello1
barplot(hello1$count, names.arg = hello1$councildistrict)
```

#####For Live Session Part 2: Freestyle!

##Install and load one of the packages given in the list for downloading APIs (or another API you have found and are interested in).
#twitteR

#install.packages("twitteR")
library("openssl")
library("httpuv")
library("twitteR")

api_key = "dEKGrIKRdziEBWCM1nqV9hZNT"
api_secret = "fnMtMIm5ucNEXELUI1ZjzgHFytMranfnKXql4iM2emf9I6TgB3"
access_token = "90782651-ndwTyAHmde9khlMPibuv4w4FLE2no0nlI0wAMpAg2"
access_token_secret = "iwfSbQb1eGfrLJbw7tattBQrnKn0gmUasfJwuD4RRGMqR"

setup_twitter_oauth(api_key, api_secret, access_token, access_token_secret)
origop <- options("httr_oauth_cache")
options(httr_oauth_cache = TRUE)
##error code
print('Error in check_twitter_oauth() : OAuth authentication error:
This most likely means that you have incorrectly called setup_twitter_oauth()')
tweets = searchTwitter("$appl", n = 10, lang = "en")

##rtweet
library("rtweet")
## name assigned to created app
appname <- "rtweet_token"
## api key (example below is not a real key)
key <- "XYznzPFOFZR2a39FwWKN1Jp41"
## api secret (example below is not a real key)
secret <- "CtkGEWmSevZqJuKl6HHrBxbCybxI1xGLqrD5ynPd9jG0SoHZbD"
twitter_token <- create_token(
    app = appname,
    consumer_key = key,
    consumer_secret = secret)
## error code
print('Warning: `create_token()` was deprecated in rtweet 1.0.0.
See vignette('auth') for detailsError in httr::init_oauth1.0(endpoint, app, permission = permission, is_interactive = is_interactive,  : 
  Unauthorized (HTTP 401).')